---
title: "Plotting Lab 2"
author: "Kevin Cabrera"
date: "1/29/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
plot.diamonds <- ggplot(diamonds, aes(clarity, fill = cut)) + geom_bar() +
  theme(axis.text.x = element_text(angle=70, vjust=0.5))
plot.diamonds
```

```{r}
ggsave("diamonds.tif",device="tiff", dpi = 600)
```

```{r}
library(ggpubr)
ggpubr::ggarrange(plot.diamonds, 
          ggarrange(plot.diamonds, plot.diamonds, nrow = 2),
          ncol = 2)
```
What is the key function?
> ggarrange

How do you flip the column/row layout?
> flip the order you put your inputs in

```{r}
ggpubr::ggarrange(ggarrange(plot.diamonds, plot.diamonds, nrow = 2), 
          plot.diamonds,
          ncol = 2)
```

Can you do this with the egg package? (I couldn’t!)
```{r}
library(egg)
grid.arrange(grobs = list(plot.diamonds,plot.diamonds,plot.diamonds), 
             layout_matrix = cbind(c(1),c(2,3)))
```
Is there something weird about these two packages?
> Yes, they both use the same 'ggarrange' function which means that if you want to use one pulling from a specific package you have to specify which one.


# Using R on the Command Line
```{r}
readr::write_delim(diamonds, path = "/Users/cabweebwub/Desktop/EE283/diamonds")
```

##Makes plot with ordered inputs on the command line##
```{r}
library(ggplot2)
library(readr)
library(dplyr)

x = commandArgs(trailing = T)

infile = x[1]
outfile = x[2]

y =read_delim(infile, delim = " ") 
  plot.diamonds <- ggplot(y, aes(clarity, fill = cut)) + geom_bar() +
  theme(axis.text.x = element_text(angle=70, vjust=0.5))
ggsave(outfile, plot = plot.diamonds, device = "pdf")

```
##Command to run the script on the command line
## > Rscript make_plot.R diamonds test1


##Runs R script with explicitly defined inputs on the command line##
```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(optparse)

option_list <- list(
make_option(c("-i", "--infile"), action="store", dest = "infile", type = "character"),
make_option(c("-o", "--outfile"), action="store", dest = "outfile", type = "character")
)

opt <- parse_args(OptionParser(option_list=option_list))

y =read_delim(opt$infile, delim = " ") 
plot.diamonds <- ggplot(y, aes(clarity, fill = cut)) + geom_bar() +
  theme(axis.text.x = element_text(angle=70, vjust=0.5))
ggsave(opt$outfile, plot = plot.diamonds, device = "pdf")

```


```{r}
library(reticulate)
use_python("/Users/cabweebwub/anaconda3/bin/python3")
```

```{r}
pd <- import("pandas", convert=F)
x = data.frame(x=rnorm(100),y=rnorm(100))
y = pd$DataFrame(r_to_py(x))
z = py_to_r(y$describe())
print(z)
```

```{python}
import pandas as pd
x = pd.read_csv("data2.txt",sep=" ")
```

```{r}
py$x
```

## This reticulate stuff isn't really working for me??

